---
title: "peer_assignment_1"
author: "Kyle Scully"
date: "August 16, 2014"
output: html_document
---

# Introduction

It is now possible to collect a large amount of data about personal
movement using activity monitoring devices such as a
[Fitbit](http://www.fitbit.com), [NikeFuelband](http://www.nike.com/us/en_us/c/nikeplus-fuelband),
or [Jawbone Up](https://jawbone.com/up). These type of devices are part of
the "quantified self" movement -- a group of enthusiasts who take
measurements about themselves regularly to improve their health, to
find patterns in their behavior, or because they are tech geeks. But
these data remain under-utilized both because the raw data are hard to
obtain and there is a lack of statistical methods and software for
processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring
device. This device collects data at 5 minute intervals through out the
day. The data consists of two months of data from an anonymous
individual collected during the months of October and November, 2012
and include the number of steps taken in 5 minute intervals each day.

## Loading and preprocessing the data

```{r}
if (!file.exists("./activity.csv")){
  download.file(
		"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",
		destfile = "./repdata-data-activity.zip",
		method = "curl"
  )

	unzip("./repdata-data-activity.zip")
}

data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
library(ggplot2)

total_steps <- tapply(data$steps, data$date, sum )

qplot(
  total_steps,
  binwidth = 706,
  xlab="total number of steps taken each day"
)
range(total_steps, na.rm=TRUE)
mean(total_steps, na.rm=TRUE)
median(total_steps, na.rm=TRUE)
```


## What is the average daily activity pattern?

## Imputing missing values

## Are there differences in activity patterns between weekdays and weekends?
